---
title: "Assignment"
author: "Juan Pablo NAVARRO RUEDA - 20021160"
date: "`r format(Sys.time(),'%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1.

By including this statement, I Juan Pablo Navarro Rueda verify that:

+ I hold a copy of this assignment that I can produce if the original is lost or damaged.
+ I hereby certify that no part of this assignment has been copied from any other student’s work or from any other source except where due acknowledgement is made in the assignment.
+ No part of this assignment has been written/produced for me by another person except where such collaboration has been authorised by the subject lecturer/tutor concerned.
+ I am aware that this work may be reproduced and submitted to plagiarism detection software programs for the purpose of detecting possible plagiarism (which may retain a copy on its database for future plagiarism checking).
+ I hereby certify that I have read and understand what the School of Computing, Engineering and Mathematics defines as minor and substantial breaches of misconduct as outlined in the learning guide for this unit.

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
